Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-12 Response.tex

The sentence has been modified as follows.

\begin{correction}

Finally, there is no closed form analytical solution for the three-body problem and there are an insufficient number of analytical constants~\cite{szebehely1967}.
As a result numerical methods are often required to investigate solutions to the three body problem.
\end{correction}

\item 
    \begin{itshape}
"These techniques suffer from numerical instability and energy drift behaviors which make them ill-suited for long-term propagation. These dissipative effects are even more detrimental with the addition of low-thrust propulsion to the dynamic equations of motion."  It really depends on what you mean by "long term".  If transfers are on the order of hundreds of days, then high precision runge-kutte integrator, for example a Runge-Kutte Verner 8(9), can maintain suitable accuracy such that the energy drift in the Hamiltonian is very small, as can be seen in some of the references that the authors have cited.  If, on the other hand you mean 10-100's of years or more, i.e., when you create your Poincare maps, then this drift is more apparent.  I think that this statement needs to be quantified better because it gives a dishonest portrayal of high-precision Runge-Kutte integrators without numbers attached to it.
\end{itshape}

\item
    \begin{itshape}
"Conventional integration techniques fail to capture the physical laws and geometric properties of the dynamic system [8]. As a result, the long term effects of low-thrust on the spacecraft trajectory are not accurately captured."  Again, I think situationally I would disagree.  Transfers on the order of 100's of days can maintain accuracies of 1e-10 (nondimensional units) in the Hamiltonian, which is generally considered a "small" amount of energy drift.
\end{itshape}

@@

\item 
    \begin{itshape}
-"The Poincare section reduces the dimensionality of the system dyanmics to the study of a related discrete update map." It does, but at the expense if a large up-front computational run that must be run well in advance to capture the problem characteristics.  Also, it is more challenging to execute in 3D, which should be noted.
\end{itshape}

Some additional detail has been included mentioning the difficulties in applying the \Poincare~section approach to the 3D case.

\begin{correction}
While the \Poincare~section is well defined for the planar case, as a 2D representation, it is more challenging to implement and visualize for the general 3D three-body problem.
\end{correction}

\item
    \begin{itshape}
-"This discrete update map, or variational integrator, shares the same geometric properties of the continuous time system and exhibits much better energy behavior than the traditional integration methods, especially over long transfer durations with small magnitude control inputs."  Yes, but the order of the variational integrator still matters.  The drift in the state vector accuracy is still important to a mission designer, even if it is guaranteed to lie on an energy surface.  I think you should indicate that this is more for preliminary analysis to characterize the transfers, when this drift in state vector accuracy is tolerable.  I.E., it's useful for the introductory phases of mission design when trying to globally characterize the design space.  Characterizing the scope of the analysis in this way would be helpful to the audience.
\end{itshape}

\item 
    \begin{itshape}
"Optimal solutions are generally sensitive to small variations in the initial multipliers. As a result, the numerical stability of sensitivity derivatives is critical to accuracy and computational performance."  I don't agree that this implies that variational integrators are better for gradient-based methods.  The primary issue is that gradient-based methods that are solving optimal control problems are using first-order approximations to iterate on the problem.  The first-order approximation is what is poor, not necessarily the gradients.  Even if these gradients are of exact accuracy (and I agree that they should always be as accurate as possible), the first-order methods in the chaotic problem are what give the difficulties.  One could use a variational or standard integrator in a first-order gradient based method and nothing will change the fact that the method will be highly sensitive, save for partitioning the sensitivities as you did with your multiple shooting approach.  At best, you can change the statement to indicate that the accuracy in the gradients may improve, which is always helpful to gradient-based methods, but it's no guarantee that it eliminates major problem sensitivity.
\end{itshape}

\item
    \begin{itshape}
Authors may also want to point out the loss of accuracy in variable step integrators that can also degrade first-order gradient based methods.  I didn't see this anywhere and it's something that should be acknowledged.  Basically, variable step integrators will introduce artificial "noise" into the gradients:

Pellegrini, E.P., Russell, R.P., On the Accuracy of Trajectory State Transition Matrices, Paper AAS-15-785, AAS/AIAA Astrodynamics Specialist Conference, Vail, CO, Aug 2015
\end{itshape}

\item 
    \begin{itshape}
"This results in an optimal solution rather than the suboptimal solution typical of direct optimal control methods." I disagree that suboptimality is typical of direct methods.  A direct method will typically solve the KKT conditions, which can be directly transcribed into the costates in the optimal control problem.  A direct method fully satisfying the KKT conditions can map to the indirect problem. If you want to strengthen this argument, then you should argue that it applies to direct methods which rely on coarse or suboptimal representations of the control.  For example, a hybrid direct method could use continuous optimal control theory control law, but directly minimize the cost function instead of solving the full TPBVP.  
\end{itshape}

@@

\item 
    \begin{itshape}
Section 5 - This method, while very useful in its given context is highly dependent on the use of the PCRTB in the framework of the current analysis.  This needs to somehow be conveyed.  3D transfers are significantly more challenging when it comes to exploiting Poincare sections.  It can be done, but more subplots, dimensions, and data storing are necessary to view the subspace - save to say, it is a more challenging endeavor that must be acknowledged for general purpose low-thrust mission design.
\end{itshape}

An additional paragraph has been added to the beginning of the section which discusses our reachability based transfer approach.
This additional content is copied below.

\begin{correction}
The numerical examples presented in this section are designed in the context of the PCRTBP.
The dynamic environment has a four dimensional state space and offers a convient integration constant in the form of the Jacobi integral.
As a result, there are well defined methods to define and exploit \Poincare sections, which result in straightforward two-dimensional subspaces of the system.
Our approach uses the \Poincare section to approximate the reachability set on this reduced subspace.
As a result, this approach is more difficult to apply to three-dimensional transfers in the general three body problem.
\Poincare sections in the case of the general six dimensional state space are significantly more challenging and typically require more complicated visualization techniques. 
However, this is an area of active research and some of the authors future research is aimed at implementing this approach for non-planar transfer trajectories.
\end{correction}

\item
    \begin{itshape}
Figures 10D and 13D - the authors need to present these plots in dimensional coordinates so that they may be reconciled with what existing technology can produce.  I recommend Newtons or milliNewtons.  For example, the NEXT (NASA evolutionary xenon thruster) can produce 0.25 Newtons of thrust at maximum power (~7 kW).  The XR5 Hall thruster can produce comparable thrust at 4.5 kW of power.  These are currently the highest-power single engines other than the ARM Hall thruster which is not flight ready yet.  For these examples to be reconciled against the capability of existing technology, we need to see the required forces that are being demanded from the optimal control problem.  It may be that the results are beyond the scope of current technology - that's fine - just say that they are examples and that it's ongoing work to formulate example problems that capture existing technology better.
\end{itshape}

\item
    \begin{itshape}
"The multiple shooting method is implemented in this paper which alleviates many of the issues associated with single shooting approaches."  Did the authors attempt single shooting for their example problems before coming to this conclusion?  With proper scaling, and problem formulation, there are examples in the literature of single shooting yielding robust results.

@@

Example: 
Ranieri, C. and Ocampo,C..  "Indirect Optimization of Spiral Trajectories", Journal of Guidance, Control, and Dynamics, Vol. 29, No. 6 (2006), pp. 1360-1366.

So, justification for its selection may be warranted.  You could always find a reference in which this trade space was really explored thoroughly to show why you made the choice.
\end{itshape}

\item
    \begin{itshape}
"In this work, we use the Matlab nonlinear solver fsolve to solve the system of nonlinear equations defined by the multiple shooting algorithm."  Can authors give some additional details?  Which fsolve algorithm? trust region dogleg,  trust region, or Levenberg-Marquardt?  Which additional options?  E.g. various tolerances.  For users of this method it's also useful to see the iteration history (more comments on this later).
\end{itshape}

\item
    \begin{itshape}
Did the authors experiment with the number of multiple shooting stages in their example problems?  There must be some sort of "sweet spot" in number of stages for the example problems attempted.  If I missed it, I apologize, but I didn't see it.
\end{itshape}

\item 
    \begin{itshape}
Section 6.1 - I don't think you need to explain how you created the three-body orbits.  This can be found in many references - You can just cite a reference and give the orbit specifications.  (Starting with line 49, page 18, up to line 21 page 19.)
\end{itshape}

\item
    \begin{itshape}
"We define a maximum magnitude of the thrust as umax = 0.75 and assume we can point the thrust in any direction within the plane." And  "we again assume a upper bound on the thrust magnitude of umax = 0.75."  What was the reason behind this? Isn't this a pretty large value of dimensional acceleration for your problem of interest?  Even if it's chosen for demonstrative purposes, there should be some sort of explanation as to why.  In the context of what electric propulsion systems can deliver, it could be arguable that this value isn't really "low-thrust" but "finite-thrust".
\end{itshape}

\item 
    \begin{itshape}
Is this method exceptionally difficult to adapt to create a numerical example from LEO or GTO?  These would be the most pragmatically interesting departure orbits to the mission design community.  Section 6.2 presents an example from GEO, but it is unlikely that GEO represents a "typical" parking orbit, since there is no reason to insert a spacecraft into GEO before it transfers to the destination orbit.  This should be called out in the conclusions or future work.
\end{itshape}

\item 
    \begin{itshape}
The authors should discuss some statistics of the convergence of their multiple shooting TPBVP - number of iterations, compute time, etc.
\end{itshape}

\item 
    \begin{itshape}
Can any intuition be gained from reporting the optimal converged cost function values in section 6.1 and 6.2?  One could at least compare them to compare the reachability in the two different examples.
\end{itshape}

\item
    \begin{itshape}
"Low energy transfers from the Earth to the Lagrange points are necessary for future missions."  One must be careful not to confuse these with traditional "low-energy transfers" to the moon, which use Sun third-body perturbations to transfer into lunar orbit.  These are what many mission designers define as "low-energy" lunar transfers.  This is actually a four-body problem (Sun, Earth, moon, spacecraft), and represents additional delta-V savings (as was done with NASA's GRAIL mission.)

@@

Example:

Parker, J. and Anderson, R., "Low-Energy Lunar Trajectory Design," DEEP SPACE COMMUNICATIONS AND NAVIGATION SERIES, Jet Propulsion Laboratory Pasadena, California, July 2013.

Online Copy: https://descanso.jpl.nasa.gov/monograph/series12/LunarTraj--Overall.pdf
\end{itshape}

\item 
    \begin{itshape}
For what it's worth, exploiting sun perturbations with low-thrust in the Earth-moon RTBP would be highly beneficial and represent a worthy avenue of future research (more on this below.)
\end{itshape}

\item 
    \begin{itshape}
The conclusions of the paper should acknowledge other potentially limiting factors of the presented analysis
-Omits advantage of exploiting fourth body perturbation (Sun in Earth/moon RTBP)
-Transfers are 2D only, method is more challenging to adapt to 3D
-Presented control magnitudes are dimensionally large, and more work is needed to determine feasibility of approach for lower accelerations
-Thrust and mass are completely decoupled from the analysis, which is limiting in terms of finding suitable hardware that can deliver the controls needed, as currently presented.
\end{itshape}

### 2017-07-12 Response.tex

For example -

Figure 2.4
Lew, A., Marsden, J., Ortiz, M., West, M., "An Overview of Variational Integrators," FINITE ELEMENT METHODS: 1970's AND BEYOND L.P. Franca (Ed.) c CIMNE, Barcelona, Spain 2003.

Online copy:
http://lagrange.mechse.illinois.edu/pubs/LeMaOrWe2004/LeMaOrWe2004.pdf
\end{itshape}

The comparison plot has been modified to follow the precedent in the literature.
The plot has been modified to show the energy deviation as a function of computational time for both the variational integrator and \texttt{ODE45}.
The modified content is copied below.
\begin{correction}
\begin{figure} 
        \centering 
        \begin{subfigure}[h]{0.5\textwidth} 
                \includegraphics[width=\textwidth]{trajectory} 
                \caption{Earth-Moon three-body trajectory used for integrator comparision}
        \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
%       \begin{subfigure}[htbp]{0.3\textwidth} 
%               \includegraphics[width=\textwidth]{components} 
%               \caption{State \( \parenth{x , y, \dot{x}, \dot{y}}\)} \label{fig:compare_components} 
%       \end{subfigure} ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
        \begin{subfigure}[htbp]{0.5\textwidth} 
                \includegraphics[width=\textwidth]{figures/cputimevsE.pdf} 
                \caption{Mean Jacobi integral deviation between variational integrator and Matlab \texttt{ODE45}} 
        \end{subfigure} 
        \caption{Integrator Comparison}
\end{figure}
A simulation comparing the variational integrator to a conventional Runge-Kutta method is given in~\cref{fig:integrator_compare}.
A particle is simulated from an initial condition of \( \vecbf{x}_0 = \begin{bmatrix} 0.75 & 0 & 0 & 0.2883\end{bmatrix}^T \) for \( t_f = 200 \approx 15\) years in the Earth-Moon system.
    The variational integrator uses a range of step sizes between \SIrange{4.72}{472}{\second} while the Runge-Kutta method uses a variable step size implemented via \texttt{ODE45} in Matlab.
    The step size of the variable integrator is varied to approximately match the run time required by the conventional \texttt{ODE45} integrator.
\Cref{fig:compare_trajectory} shows the trajectory of the spacecraft in the rotating reference for this comparison.
Both integration schemes result in trajectories that are initially nearly identical.
\Cref{fig:compare_energy} shows the mean Jacobi integral deviation over the entire simulation time as a function of computation time.
For a given computational effort, in the form of simulation run time, the variational integrator will provide a smaller energy deviation as compared to the convential integration scheme.
Over long simulation horizons or with the addition of small control inputs the inability of conventional integration schemes to accurately track the system energy limits the applicability of conventional techniques in which energy conservation is mandatory for characterizing the solution space.
\end{correction}
\item 
    \begin{itshape}
It may also be generally worth acknowledging the benefits of Taylor's method within the context of variational integrators:
Schmitt, J., Shingel, T., Leok, M., "LAGRANGIAN AND HAMILTONIAN TAYLOR VARIATIONAL INTEGRATORS," eprint arXiv:1703.06599, 2017

### 2017-07-12 Response.tex

\item
    \begin{itshape}
"In this work, we use the Matlab nonlinear solver fsolve to solve the system of nonlinear equations defined by the multiple shooting algorithm."  Can authors give some additional details?  Which fsolve algorithm? trust region dogleg,  trust region, or Levenberg-Marquardt?  Which additional options?  E.g. various tolerances.  For users of this method it's also useful to see the iteration history (more comments on this later).
\end{itshape}

\item
    \begin{itshape}
Did the authors experiment with the number of multiple shooting stages in their example problems?  There must be some sort of "sweet spot" in number of stages for the example problems attempted.  If I missed it, I apologize, but I didn't see it.
\end{itshape}

\item 
    \begin{itshape}
Section 6.1 - I don't think you need to explain how you created the three-body orbits.  This can be found in many references - You can just cite a reference and give the orbit specifications.  (Starting with line 49, page 18, up to line 21 page 19.)
\end{itshape}

The discussion of generating periodic orbits in the three body problem has been removed.
It replaced with a small introduction mentioning the differential correction process and a citation to a relevant resource. 
The revised paragraph is copied below.

\begin{correction}
The first objective is to design a transfer trajectory from a planar periodic orbit about the \( L_1\) Lagrange point to a bounded orbit in the vicinity of the Moon.
The target region is created by choosing an initial condition of \( x_0 = \begin{bmatrix}1.05 & 0 & 0 & 0.35 \end{bmatrix}^T \) with \( \mu = 0.0125 \).
The target set is propagated over a period of \( t = \num{20} \) in non-dimensional units which corresponds to approximately \num{1.5} years.
\Cref{fig:moon_orbit} shows that the target set remains in the vicinity of the Moon, or \( m_2\), in the rotating reference frame. 
This type of orbit would be useful for a variety of mission scenarios.
The bounded trajectories of the vehicles and constant line of sight to both the Moon and the Earth would allow for constant communication for future manned missions and potential habitats.
The initial set is a planar periodic orbit about \( L_1\), which is generated using the process of differential correction of a linear approximation~\cite{koon2011}.
\end{correction}

### 2017-07-12 Response.tex

\item
    \begin{itshape}
"The multiple shooting method is implemented in this paper which alleviates many of the issues associated with single shooting approaches."  Did the authors attempt single shooting for their example problems before coming to this conclusion?  With proper scaling, and problem formulation, there are examples in the literature of single shooting yielding robust results.

Example: 
Ranieri, C. and Ocampo,C..  "Indirect Optimization of Spiral Trajectories", Journal of Guidance, Control, and Dynamics, Vol. 29, No. 6 (2006), pp. 1360-1366.

So, justification for its selection may be warranted.  You could always find a reference in which this trade space was really explored thoroughly to show why you made the choice.
\end{itshape}

Our original attempt at solving the optimal control problem did rely on single shooting.
However, during our investigation it was found that it was quite difficult for solutions to converge.
As a result, we decided to implement the multiple shooting approach in hopes of generating more consistent and robust solutions.
While it is possible to use single shooting, such as the provided reference, it is known that the single shooting approach will have greater sensitivity to initial costate errors as compared to a multiple shooting method.
This can be alleviated, or entirely mitigated in the case of~\cite{ranieri2006}, it is highly case specific and dependent on a large variety of case specific techniques. 
For example, the work in~\cite{ozimek2010a} used both a single shooting and multiple shooting approach to solve the optimal control problem.
The large sensitivity of the single shooting approach was mitigated through the use of the multiple shooting method, at the expense of additional design variables.

In the manuscript, additional detail has been added in this section which describes the difficulties of the single shooting approach and our decision to use the multiple shooting method.
The modified portion of the manuscript is copied here.
\begin{correction}
Rather than numerical integration over the entire time interval, multiple shooting segments the interval into several smaller sub-arcs~\cite{stoer2013}.
This multiple shooting approach incorporates additional interior constraints but reduces the sensitivity of the costates along each sub-arc.
The use of the multiple shooting method reduces the sensitivity of changes in the initial costate at the expense of additional design variables, but has been shown to provide more stable and robust solutions~\cite{ozimek2010a}.
\end{correction}

### 2017-07-12 manuscript.tex
Add some detail on the time units
Add some justification for the multiple shooting approach
Reviewer 1 Comment 28

The optimal control formulation presented in this section results in a two point boundary value problem (TPBVP). 
There exist many methods to solve TPBVPs such as gradient, quasilinearization, and shooting methods~\cite{bryson1975,kirk2012}.
Shooting methods are common in astrodynamic trajectory design problems and relatively simple to implement.
In the shooting method, initial conditions are varied such that a terminal constraint is satisfied, similar to the way an archer modifies the bow in order to more accurately strike a target. 
Consider the vector of initial conditions, \( \vecbf{\chi} = \braces{\vecbf{x}_0, \vecbf{\lambda}_0}\), which is varied to satisfy some terminal constraints of the form \( \vecbf{G}(\vecbf{\chi}) = \braces{\vecbf{x}_t - \vecbf{x}_n} = 0 \).
The free variables at the terminal time are computed by propogation of \( \vecbf{\chi} \) over the selected time horizon. 
At the terminal time, the constraint vector is calculated and if not satisfied \( \vecbf{\chi}\) is varied.
Rather than numerical integration over the entire time interval, multiple shooting segments the interval into several smaller sub-arcs~\cite{stoer2013}.
The multiple shooting method is implemented in this paper which alleviates many of the issues associated with single shooting approaches.

@@

% invariant manifold transfer
As a source for comparison, the method of using invariant manifolds, introduced in~\cite{koon2011}, is implemented.
As described in~\cref{sec:invariant_manifold}, these invariant manifolds are the set of trajectories that either asymptotically arrive or depart the periodic orbit. 
We generate the unstable manifold associated with the initial planar periodic orbit.
We numerically propagate the unstable manifold forward in time until the trajectories intersect the \Poincare section \( y = 0 \).
\Cref{fig:manifold_trajectory} shows the unstable invariant manifold generated from the initial \( L_1\) periodic orbit. 
The blue points in~\cref{fig:manifold_poincare} are the intersections of the target Moon orbit and the \Poincare section.
The two circular regions are the ascending (right) and descending (left) intersections of the target orbit and \Poincare section.
The green points in~\cref{fig:manifold_poincare} are intersections of the unstable manifold from~\cref{fig:manifold_trajectory} with the \Poincare section \( y = 0 \).
Only a single branch of the invariant manifold intersects with the ascending region of the target orbit.
There are no intersections of the invariant manifold with the descending region of the target orbit.
The numerical values associated with the green points denote the required time of flight along the invariant manifold in non-dimensional units.
The required travel time for a transfer using the unstable invariant manifold is \( t_f \approx 3.1\).
\begin{figure} 
        \centering 
        \begin{subfigure}[htbp]{0.5\textwidth} 
                \includegraphics[width=\textwidth]{manifold_trajectory} 
                \caption{Invariant Manifold} \label{fig:manifold_trajectory} 
        \end{subfigure}~ %
        \begin{subfigure}[htbp]{0.5\textwidth} 
                \includegraphics[width=\textwidth]{manifold_poincare} 
                \caption{Poincar\`e Section} \label{fig:manifold_poincare} 
        \end{subfigure} 
        \caption{Invariant manifold transfer}
        \label{fig:invariant_manifold_transfer} 
\end{figure}

>>>>

The optimal control formulation presented in this section results in a two point boundary value problem (TPBVP). 
There exist many methods to solve TPBVPs such as gradient, quasilinearization, and shooting methods~\cite{bryson1975,kirk2012}.
Shooting methods are common in astrodynamic trajectory design problems and relatively simple to implement.
In the shooting method, initial conditions are varied such that a terminal constraint is satisfied, similar to the way an archer modifies the bow in order to more accurately strike a target. 
Consider the vector of initial conditions, \( \vecbf{\chi} = \braces{\vecbf{x}_0, \vecbf{\lambda}_0}\), which is varied to satisfy some terminal constraints of the form \( \vecbf{G}(\vecbf{\chi}) = \braces{\vecbf{x}_t - \vecbf{x}_n} = 0 \).
The free variables at the terminal time are computed by propogation of \( \vecbf{\chi} \) over the selected time horizon. 
At the terminal time, the constraint vector is calculated and if not satisfied \( \vecbf{\chi}\) is varied.
Rather than numerical integration over the entire time interval, multiple shooting segments the interval into several smaller sub-arcs~\cite{stoer2013}.
This multiple shooting approach incorporates additional interior constraints but reduces the sensitivity of the costates along each sub-arc.
The use of the multiple shooting method reduces the sensitivity of changes in the initial costate at the expense of additional design variables, but has been shown to provide more stable and robust solutions~\cite{ozimek2010a}.

@@

% invariant manifold transfer
As a source for comparison, the method of using invariant manifolds, introduced in~\cite{koon2011}, is implemented.
As described in~\cref{sec:invariant_manifold}, these invariant manifolds are the set of trajectories that either asymptotically arrive or depart the periodic orbit. 
We generate the unstable manifold associated with the initial planar periodic orbit.
We numerically propagate the unstable manifold forward in time until the trajectories intersect the \Poincare section \( y = 0 \).
\Cref{fig:manifold_trajectory} shows the unstable invariant manifold generated from the initial \( L_1\) periodic orbit. 
The blue points in~\cref{fig:manifold_poincare} are the intersections of the target Moon orbit and the \Poincare section.
The two circular regions are the ascending (right) and descending (left) intersections of the target orbit and \Poincare section.
The green points in~\cref{fig:manifold_poincare} are intersections of the unstable manifold from~\cref{fig:manifold_trajectory} with the \Poincare section \( y = 0 \).
Only a single branch of the invariant manifold intersects with the ascending region of the target orbit.
There are no intersections of the invariant manifold with the descending region of the target orbit.
The numerical values associated with the green points denote the required time of flight along the invariant manifold in non-dimensional units.
The required travel time for a transfer using the unstable invariant manifold is  approximately \( t_f \approx 3.1\) non-dimensional time units.
\begin{figure} 
        \centering 
        \begin{subfigure}[htbp]{0.5\textwidth} 
                \includegraphics[width=\textwidth]{manifold_trajectory} 
                \caption{Invariant Manifold} \label{fig:manifold_trajectory} 
        \end{subfigure}~ %
        \begin{subfigure}[htbp]{0.5\textwidth} 
                \includegraphics[width=\textwidth]{manifold_poincare} 
                \caption{Poincar\`e Section} \label{fig:manifold_poincare} 
        \end{subfigure} 
        \caption{Invariant manifold transfer}
        \label{fig:invariant_manifold_transfer} 
\end{figure}
